%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Andrei Rykhlevskii

\documentclass[margin,line]{resume}
\usepackage{bibentry}
\usepackage{url}
\usepackage{xspace}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Andrei Rykhlevskii, Ph.D.}
\begin{resume}

    % Contact Information
    \section{\mysidestyle Contact\\Information}
%406 Paddock Dr W, Savoy, IL, 61874  \hfill (217) 3052385  \hfill
%Foreign address: Bykovskaya 10-40, Podolsk, Russian Federation, 142111      

    Nuclear Engineer \hfill mobile: (217) 305-2385 
    \vspace{0mm}\\\vspace{0mm}
    \hspace{-1.35mm}\textsl{Argonne National Laboratory}
        \hfill e-mail: andrewryh@gmail.com            
        \vspace{0mm}\\\vspace{0mm}%
    \textsl{Research and Test Reactors}
       
    %__________________________________________________________________________________________________________________
    % Resume Objective
    %\section{\mysidestyle Objective}
		%Seeking research and teaching opportunities in nuclear engineering and scientific computation.%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
		Nuclear systems modeling/optimization, stochastic neutronics, 
		optimization of isotopes production, research reactor 
		conversion, High Performance Computing, uncertainty quantification
	%	 scientific software development
	%	Nuclear systems modeling and analysis, reactor physics, machine 
	%	learning and artificial intelligence, High Performance Computing, 
	%	uncertainty quantification
	%    Nuclear systems thermal hydraulics and multi-physics, 
	%    accident transient analysis, scientific software development, 
	%    optimization, uncertainty quantification, High Performance 
	%    Computing
	%	Nuclear systems modeling/analysis, open-source scientific 
	%	software development, big data analytics, parallel computing, 
	%	data visualization, software optimization/performance analysis, HPC
	%	Nuclear systems modeling and analysis, reactor physics, machine 
	%	learning and artificial intelligence, High Performance Computing, 
	%	uncertainty quantification
                %
    %__________________________________________________________________________________________________________________
    % Academic Appointments
    %	 	\vspace{-2mm}
    %\section{\mysidestyle Academic\\Appointments}
    %           \vspace{-2mm}\\\vspace{-3mm}%
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle PhD}
    \textbf{University of Illinois at Urbana-Champaign}, \textsc{Nuclear 
    Engineering} \hfill\textbf{\mbox{Aug 2016 -- Aug 
    2020}}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Fuel processing simulation tool for liquid-fueled nuclear reactors
        \item Advisor:  Professor Kathryn D. Huff
        \item Concentration in Computational Science and Engineering
    \end{list2}\vspace{-1.5mm}
    \section{\mysidestyle MSc}
    \textbf{University of Illinois at Urbana-Champaign}, \textsc{Nuclear Engineering} \hfill\textbf{\mbox{Aug 2016 -- May 2018}}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Advanced online fuel reprocessing simulation for thorium-fueled Molten Salt Breeder Reactor
        \item Advisor:  Professor Kathryn D. Huff
    \end{list2}\vspace{-1.5mm}
    \section{\mysidestyle MSc}
    \textbf{Financial University - Moscow, Russia}, \textsc{Financial Management} \hfill \textbf{\mbox{Oct 2011 -- Mar 2014	}}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Using stock market tools for IT-industry investments
        \item Advisor:  Professor Svetlana Grishkina
    \end{list2}\vspace{-1.5mm}
    \section{\mysidestyle BSc}
    \textbf{Bauman Moscow State Technical University},\textsc{Nuclear Engineering}\hfill \textbf{ Sep 2004 -- Jun 2010}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
	\item Calculating structural materials activation for VVER-1200 decommissioning
	\item Concentration in Computational Reactor Physics and Nuclear Fuel Cycle
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Research\\Experience}               
    \textbf{Argonne National Laboratory}, Lemont, IL\\
		\textsl{Nuclear Engineer, Core Design \& Safety Analysis Group} 
		\hfill \textbf{Jun 2021 -- present}\\		
		\textsl{Postdoctoral Appointee, Core Design \& Safety Analysis Group} 
		\hfill \textbf{Sep 2020 -- Jun 2021}\\
\vspace{-4mm}\begin{list2}
	\item Performing neutronics calculations for research reactors to 
	support conversion from HEU to LEU
	\item Developing tools for pre- and post-processing 
	to facilitate MCNP and VESTA computations
	\item Analyzing reactivity initiated accidents in Belgian Reactor 2 (BR2)
\end{list2}

    \textbf{University of Illinois at Urbana-Champaign}, Urbana, IL\\
		\textsl{Graduate Research Assistant, Advanced Reactors and Fuel Cycles 
		Group} \hfill \textbf{Aug 2016 -- Aug 2020}\\
                \vspace{-4mm}\begin{list2}
                \item Developed computational tools and models for advanced 
                reactors and fuel cycles
                \item Investigated load-following capabilities of MSRs
                \item Modeled MSR neutronics using Monte Carlo code 
                Serpent
				\item Created MSR models in multi-physics environment MOOSE
				\item Generated problem-oriented nuclear data libraries using 
				Serpent, SCALE, OpenMC
                \end{list2}

    \textbf{Oak Ridge National Laboratory}, Oak Ridge, TN\\
		\textsl{NESLS Intern -- Reactor Physics Group} \hfill \textbf{May 2018 
		-- Aug 2018}\\
                \vspace{-4mm}\begin{list2}
                \item Developed a various Fast Spectrum Molten Salt Reactor 
                neutronics models (SCALE, Serpent)
				\item Implemented and tested continuous online separation and 
				feeds for MSR
				\item Analyzed MSR fuel cycle performance in comparison with 
				Sodium-cooled Fast Reactors
                \end{list2}

    \textbf{OKB GIDROPRESS (State Atomic Energy Corporation ``ROSATOM")}, 
    Russia \\
		\textsl{Lead Engineer} \hfill \textbf{Dec 2015 -- Jul 2016}\\
                Extending life cycle of Nuclear Power Plants (NPP) with 
                VVER-440

    \textbf{BUKO Ltd}, Podolsk, Russia \hfill \textbf{Sep 2014 -- Dec 2015}\\
		\textsl{Financial analyst}\\
		Developed and applied robots (C\#, VB) for algorithmic trading

    \textbf{Svyaz Standart Ltd}, Podolsk, Russia \hfill \textbf{Feb 2012 -- Aug 2014}\\
		\textsl{Chief Technology Officer}\\
		Designed and managed Internet Service Provider (ISP) metro networks

    \textbf{OKB GIDROPRESS (State Atomic Energy Corporation ``ROSATOM")}, 
    Russia \\
		\textsl{Nuclear Engineer} \hfill \textbf{Nov 2009 -- Feb 2012}\\
                \vspace{-4mm}\begin{list2}
				\item Performed neutronics calculations for expending 
				operation period of Balakovo and Kola NPPs
				\item Analyzed decommissioning for the Preliminary Safety 
				Analysis Report of Belene NPP, Bulgaria
				\item Performed simulations for V\&V and certification of  
				KATRIN-2.0 deterministic $S_N$ code
				\item Developed a MATLAB code for processing neutron flux data 
				collected from NPPs
                \end{list2}

		%__________________________________________________________________________________________________________________
	% Honors and Awards
	\section{\mysidestyle Honors and\\Awards}
	Kuck Computational Science \& Engineering Scholarship\hfill 
	\textbf{2019-2020}\vspace{.5mm}\\%
	American Nuclear Society, John and Muriel Landis Scholarship\hfill 
	\textbf{2017-2020}\vspace{.5mm}\\%
	Podolsk city council innovative entrepreneurship award\hfill 
	\textbf{2014}\vspace{.5mm}\\%
	Graduated FU with high distinction (highest graduation 
	honor)                \hfill \textbf{2014}\vspace{.5mm}\\%
	Graduate scholarship for excellent students, 
	FU                       	\hfill \textbf{2013}\vspace{.5mm}\\%
	Research achievement award, OKB 
	GIDROPRESS                                   
	\hfill\textbf{2011}\vspace{.5mm}\\%
	Academic scholarship for distinguished student, 
	BMSTU		                 \hfill\textbf{2008--2010}\vspace{.5mm}\\%
	Student Professional Society scholarship, 
	BMSTU                                \hfill\textbf{2004--2010}%
 
    \section{\mysidestyle Journal\\Publications}
      \begin{bibenum}
        \item Ashraf, O., \textbf{Rykhlevskii, A.}, Tikhomirov, G.V., Huff, 
      	K.D. ``Preliminary design of control rods in the single-fluid 
      	double-zone thorium molten salt reactor (SD-TMSR).''
      	\textbf{Annals of Nuclear Energy}, vol. 152. 
      	\url{https://doi.org/10.1016/j.anucene.2020.108035}, March 
      	2021.  	
	    \item Ashraf, O., \textbf{Rykhlevskii, A.}, Tikhomirov, G.V., Huff, 
		K.D. ``Strategies for thorium fuel cycle transition in the SD-TMSR.''
		\textbf{Annals of Nuclear Energy}, vol. 148. 
		\url{https://doi.org/10.1016/j.anucene.2020.107656}, December 
		2020.   	
 		\item Bae, J.W., \textbf{Rykhlevskii, A.}, Chee, G., Huff, K.D. ``Deep 
		 Learning Approach to Nuclear Fuel Transmutation in a Fuel Cycle 
		 Simulator.'' \textbf{Annals of Nuclear Energy}, vol. 139. 
		 \url{https://doi.org/10.1016/j.anucene.2019.107230}, May 2020.
	    \item Ashraf, O., \textbf{Rykhlevskii, A.}, Tikhomirov, G.V., Huff, 
		K.D. ``Whole core analysis of the single-fluid double-zone thorium 
		molten salt reactor (SD-TMSR).'' \textbf{Annals of Nuclear Energy}, 
		vol. 137. \url{https://doi.org/10.1016/j.anucene.2019.107115}, March 
		2020.
	    \item \textbf{Rykhlevskii, A.}, Bae, J.W., Huff, K. ``Modeling And 
	    Simulation of Online Reprocessing in the Molten Salt Breeder 
	    Reactor.'' \textbf{Annals of Nuclear Energy}, vol. 128, Pages 366 - 
	    379. \url{https://doi.org/10.1016/j.anucene.2019.01.030}, June 2019.
       \item Lindsay, A., Ridley, G., \textbf{Rykhlevskii, A.}, Huff, K. ``Introduction to 
               Moltres: an Application for Simulation of Molten Salt 
               Reactors.''  \textbf{Annals of Nuclear Energy}, vol. 114, Pages 
               530 - 540. \url{doi.org/10.1016/j.anucene.2017.12.025}, April 
               2018.
       %\item Scopatz,~A., Gidden,~M., Carlsen,~R., Flanagan,~R.,
       %\textbf{Huff,~K.}, McGarry,~M., Opotowsky,~A., Rakhimov,~O., Welch,~Z.,
       %Wilson,~P.  ``\Cyclus Archetypes'', 2015.
       %\url{http://arxiv.org/abs/1511.05619}
      \end{bibenum}
\vspace{2mm} % add this back if you return to Refereed Journal..
%	\section{\mysidestyle Submitted}
%	\begin{bibenum}
	
%	\end{bibenum}
    \section{\mysidestyle Refereed\\Conference\\Proceedings}
    \begin{bibenum}
     \item \textbf{Rykhlevskii, A.}, O'Grady, D., Kozlowski, T., Huff, K. 
     ``The Impact of Xenon-135 on Load Following Transatomic Power Molten Salt 
     Reactor.'' \textbf{Transactions of the American Nuclear Society Winter 
     Meeting.} Washington, DC, United States, 2019.
     \item Park, S.M., \textbf{Rykhlevskii, A.}, Huff, K. 
	``Safety Analysis of the Molten Salt Fast Reactor Fuel Composition Using 
	Moltres.'' \textbf{Proc. GLOBAL International Fuel Cycle Conference.} Seattle, WA, United States, September 2019.    
     \item Betzler, B.R., \textbf{Rykhlevskii, A.}, Worrall, A., Huff, K. 
     ``Impacts of Fast Spectrum Molten Salt Reactor Characteristics on Fuel 
     Cycle Performance.'' \textbf{Proc. GLOBAL International Fuel Cycle 
     Conference.} Seattle, WA, United States, September 2019.    
    \item \textbf{Rykhlevskii, A.}, Betzler, B.R., Worrall, A., Huff, K. ``Fuel Cycle Performance of Fast Spectrum Molten Salt Reactors designs.'' \textbf{Proc. M\&C 2019 - International Conference on Mathematics \& Computational Methods Applied to Nuclear Science and Engineering.} 
            Portland, OR, United States, August 25-29, 2019.    
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Full-Core Analysis of Thorium-Fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code.'' 
            \textbf{Transactions of the American Nuclear Society Winter Meeting.} 
            Washington, DC, United States, 2017.
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Online Reprocessing Simulation for Thorium-Fueled Molten Salt Breeder Reactor.'' 
            \textbf{Transactions of the American Nuclear Society Winter Meeting.} 
            Washington, DC, United States, 2017.
%      \item \textbf{Rykhlevskii, A.}, Tsofin, V. ``Comparing fast neutron 
%transport calculations using code package KATRIN-2.0 for various options of 
%VVER-440 core setup.''
%         \textbf{Scientific and technical conference of young specialists.}
%         Podolsk, Russia, March 2011.
	\end{bibenum}
%__________________________________________________________________________________________________________________
% Conference Publications
    \section{\mysidestyle Refereed\\Conference\\Abstracts}
    \begin{bibenum} 
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Simulation of Molten Salt Reactors with Moltres.'' \textbf{2019 SIAM Conference on Computational Science and Engineering}, 
            Spokane, WA, February 2019.
	\item \textbf{Rykhlevskii, A.}, Betzler, B.R., Bae, J.W., Huff, K. ``Fuel Cycle Performance of Fast Spectrum Molten Salt Reactor Designs.'' (poster)
            \textbf{Oak Ridge National Laboratory Nuclear Engineering Science Laboratory Synthesis Poster Session.} 
            Oak Ridge, TN, United States, 2018.
    \item \textbf{Rykhlevskii, A.}, Huff, K. ``Computational Tools for Advanced 
            Molten Salt Reactor Simulation.'' \textbf{Blue Waters Symposium}, 
            Sun River, OR, June 2018.
	\end{bibenum}
% Technical Reports
\section{\mysidestyle Technical\\Reports}
\begin{bibenum} 
	\item \textbf{Rykhlevskii, A.} et al. ``Fuel Plate Irradiation
	in the FUTURE-5 Basket: Reactivity Insertion Transients with
	Automatic Power Reduction by the Control Rods''
	Argonne National Laboratory report ANL/RTR/TM-21/20, September 2021.
	\item \textbf{Rykhlevskii, A.}, Bergeron, A., Puig, F. ``FUTURE-HFIR 
	Irradiation Test - Complementary Beginning of Cycle Neutronics Analysis''
	Argonne National Laboratory report ANL/RTR/TM-21/4, March 2021.
	\item \textbf{Rykhlevskii, A.}, Huff, K. ``Milestone 2.1 Report: 
	Demonstration of 
	SaltProc.'' \textbf{Advanced Reactors and Fuel Cycles Report Series}, 
	Nuclear Plasma and Radiological Engineering, University of Illinois.  
	Report UIUC-ARFC-2019-04, \url{https://doi.org/10.5281/zenodo.3355649}, 
	June 2019.
\end{bibenum}
% Other Publications
\section{\mysidestyle Other\\Publications}
\begin{bibenum}
	\item \textbf{Rykhlevskii, A.} Fuel processing simulation tool for
	liquid-fueled nuclear reactors.
	Ph.D. dissertation. University of Illinois at Urbana-Champaign.  July 2020.
	\item \textbf{Rykhlevskii, A.} Advanced  online fuel reprocessing 
	simulation for Thorium-fueled Molten Salt Breeder Reactor.
	M.Sc. thesis. University of Illinois at Urbana-Champaign.  May 2018.
\end{bibenum}
%__________________________________________________________________________________________________________________
% Software Products
\section{\mysidestyle Software\\Products}
\begin{bibenum}
	\item \textbf{Rykhlevskii, A.}, Bae, J.W., Huff, K. ``SaltProc v0.2.'' 
	\textbf{zenodo}, July 2018.
	\url{http://dx.doi.org/10.5281/zenodo.1196454}.
	
	\item Lindsay, A., Huff, K., \textbf{Rykhlevskii, A.} ``moltres v0.1.'' 
	\textbf{zenodo}, June 2017. \url{http://dx.doi.org/10.5281/zenodo.801823}.
	
	\item Bates, C., Biondo, E., Brachem, C., Carlsen, R., Cary, J., Davis, 
	A., Dembia, C., Elfring, M., Flanagan, R., Gidden, M., Haines, T., 
	Howland, J., Huff, K., Jackson, S., Kiesling, K., Klebenow, M., Kuett, M., 
	Manalo, K., M. McCormick, A. Opotowsky, C., Pavlovsky, R., Rabbani, M., 
	Relson, E., Romano, P., \textbf{Rykhlevskii, A.}, Scopatz, A., Shriwise, 
	P., Slaybaugh, R., Wilson, P., Xia, J., J. Zachman, C., and Zweig, M. 
	``PyNE v0.5.11.'' \textbf{github}. 
	github.com/pyne/pyne/releases/tag/0.5.11. March 2018. 
\end{bibenum}
	% Invited Talks
    \section{\mysidestyle Invited Talks}
    %\textbf{<++>}, <++>, \emph{<++>}.  \hfill\textbf{<+mo+> <+date+>, 
    %<+yy+>}\\
      \textbf{ANS Winter 2020}, Chicago, IL. \emph{Lightning Talk}.  
      \hfill\textbf{Nov 17, 2020}\\
      \textbf{U. Illinois}, Nuclear, Plasma, \& Radiological Engineering. \emph{Seminar}.  \hfill\textbf{Apr 10, 2018}\\
        %__________________________________________________________________________________________________________________
    % Teaching Experience
    \section{\mysidestyle Engineering\\Teaching}
    \textbf{University of Illinois at Urbana-Champaign} \hfill \textbf{Nov 29, 2017}\\
    \textsl{Guest Lecturer}~\hfill \textbf{Nov 9, 2018}\\
    \textsc{Dept. of Nuclear, Plasma, and Radiological Engineering}\\ 
               \textsl{NPRE 247, Modeling Nuclear Energy System}\\
               UNIX Shell, Basic Scripting, Serpent usage, Monte Carlo methods
               \vspace{2mm}
    %__________________________________________________________________________________________________________________
    % Advising
    \section{\mysidestyle Undergraduate\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}  
    \makebox[0.2\textwidth][l]{\textsc{\underline{Degree - Year}}} 
    \hfill\textsc{\underline{Role}}\\
    \makebox[0.3\textwidth][l]{\textbf{Jin Whan Bae}}  
    \makebox[0.2\textwidth][l]{BS - 2017} 
    \hfill Mentor\\
    \makebox[0.3\textwidth][l]{\textbf{Louis Kissinger}}  
    \makebox[0.2\textwidth][l]{BS - 2019} 
    \hfill Mentor\\
    \section{\mysidestyle Graduate\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}  
    \makebox[0.2\textwidth][l]{\textsc{\underline{Degree - Year}}} 
    \hfill\textsc{\underline{Role}}\\
    \makebox[0.3\textwidth][l]{\textbf{Anshuman Chaube}}  
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)}
    \hfill Mentor\\
    \makebox[0.3\textwidth][l]{\textbf{Sun Myung Park}}  
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)}
    \hfill Mentor\\
    \makebox[0.3\textwidth][l]{\textbf{Gwendolyn Chee}}  
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)} 
    \hfill Mentor\\
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Scientific\\Computing\\Skills}
                \textbf{Programming} \hfill Python, bash/csh, C++, FORTRAN, 
                VB, MPI, OpenMP \vspace{.5mm}\\%
                %\textbf{Machine Learning} \hfill Keras\vspace{.5mm}\\%
                \textbf{Build Systems} \hfill make, CMake\vspace{.5mm}\\%
                \textbf{Databases} \hfill PyTables, HDF5, SQL\vspace{.5mm}\\%
                \textbf{Test Frameworks} \hfill Travis CI, 
                pytest\vspace{.5mm}\\%
                \textbf{Version Control} \hfill git\vspace{.5mm}\\%
                \textbf{Transport Software} \hfill MCNP, VESTA, OpenMC, Serpent,
                SCALE, WIMS, CNCSN 2009 \vspace{.5mm}\\%
                \textbf{Other Tools} \hfill  PARET/ANL, MOOSE, MATLAB/Octave, PyNE, 
                CYCLUS, ANSYS CFX, \LaTeX \vspace{.5mm}%
    %__________________________________________________________________________________________________________________

    \section{\mysidestyle Other\\University\\Service}
		\textbf{Judge}, HackIllinois \hfill \textbf{2020}\vspace{.5mm}\\%
		\textbf{Mentor}, HackIllinois \hfill 
		\textbf{2017}\vspace{.5mm}\\%
    %__________________________________________________________________________________________________________________
    % References

\section{\mysidestyle Editing and\\Reviewing}
    \textbf{Manuscript Referee}~\hfill \emph{Annals of Nuclear Energy}\\%
    					\mbox{}~\hfill \emph{Progress in Nuclear Energy}\\%
						\mbox{}~\hfill \emph{2019 GLOBAL International Fuel 
    Cycle Conference}\\%
%______________________________________________________________________________
\section{\mysidestyle Professional\\Service}
\textbf{Member}, American Nuclear Society  \hfill 
\textbf{2016--present}\vspace{.5mm}\\
\textbf{Member}, Society for Industrial and Applied Mathematics  \hfill 
\textbf{2018--present}\vspace{.5mm}\\%

\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

