%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Andrei Rykhlevskii

\documentclass[margin,line]{resume}
\usepackage{bibentry}
\usepackage{url}
\usepackage{xspace}

\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Andrei Rykhlevskii -- List of publications}
\begin{resume}
 
    \section{\mysidestyle Journal\\Publications}
      \begin{bibenum}
	    \item \textbf{Rykhlevskii, A.}, Bae, J.W., Huff, K. ``Modeling And 
	    Simulation of Online Reprocessing in the Molten Salt Breeder 
	    Reactor.'' \textbf{Annals of Nuclear Energy}, 
               \url{https://doi.org/10.1016/j.anucene.2019.01.030}, 
               Jun. 2019.
       \item Lindsay, A., Ridley, G., \textbf{Rykhlevskii, A.}, Huff, K. ``Introduction to 
               Moltres: an Application for Simulation of Molten Salt 
               Reactors.''  \textbf{Annals of Nuclear Energy}, vol. 114, Pages 530 - 540, 2018. \url{doi.org/10.1016/j.anucene.2017.12.025}, Apr. 2018.
       %\item Scopatz,~A., Gidden,~M., Carlsen,~R., Flanagan,~R.,
       %\textbf{Huff,~K.}, McGarry,~M., Opotowsky,~A., Rakhimov,~O., Welch,~Z.,
       %Wilson,~P.  ``\Cyclus Archetypes'', 2015.
       %\url{http://arxiv.org/abs/1511.05619}
      \end{bibenum}
\vspace{2mm} % add this back if you return to Refereed Journal..
	\section{\mysidestyle Submitted}
	\begin{bibenum}
		\item Bae, J.W., Chee, G., \textbf{Rykhlevskii, A.}, Huff, K.D. ``Deep 
		Learning Approach to Nuclear Fuel Transmutation in a Fuel Cycle 
		Simulator.'' Submitted to \textbf{Annals of 
		Nuclear Energy}, August 2019.
		\item Ashraf, O., \textbf{Rykhlevskii, A.}, Tikhomirov, G.V., Huff, 
		K.D. ``Whole core analysis of the Single-fluid Double-zone Thorium 
		Molten Salt Reactor (SD-TMSR).'' Submitted to \textbf{Annals of 
		Nuclear Energy}, May 2019.
	\end{bibenum}
    \section{\mysidestyle Refereed\\Conference\\Proceedings}
    \begin{bibenum}
     \item \textbf{Rykhlevskii, A.}, O'Grady, D., Kozlowski, T., Huff, K. 
     ``The Impact of Xenon-135 on Load Following Transatomic Power Molten Salt 
     Reactor.'' Submitted to 
		 \textbf{American Nuclear Society Winter Meeting.} Washington, DC, 
		 United States, 2019.
     \item Park, S.M., \textbf{Rykhlevskii, A.}, Huff, K. 
	``Safety Analysis of the Molten Salt Fast Reactor Fuel Composition Using 
	Moltres.'' \textbf{Proc. GLOBAL International Fuel Cycle 
		Conference.} Seattle, WA, United 
	States,	September 2019.    
     \item Betzler, B.R., \textbf{Rykhlevskii, A.}, Worrall, A., Huff, K. 
     ``Impacts of Fast Spectrum Molten Salt Reactor Characteristics on Fuel 
     Cycle Performance.'' \textbf{Proc. GLOBAL International Fuel Cycle 
     Conference.} Seattle, WA, 
     United States, September 2019.    
    \item \textbf{Rykhlevskii, A.}, Betzler, B.R., Worrall, A., Huff, K. 
    ``Fuel Cycle Performance of Fast Spectrum Molten Salt Reactors designs.'' 
    \textbf{Proc. M\&C 2019 - International Conference on Mathematics \& 
    Computational Methods Applied to Nuclear Science and Engineering.} 
            Portland, OR, United States, August 25-29, 2019.    
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Full-Core Analysis of Thorium-Fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code.'' 
            \textbf{Transactions of the American Nuclear Society Winter 
            Meeting.} 
            Washington, DC, United States, 2017.
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Online Reprocessing Simulation for Thorium-Fueled Molten Salt Breeder Reactor.'' 
            \textbf{Transactions of the American Nuclear Society Winter 
            Meeting.} 
            Washington, DC, United States, 2017.
      \item \textbf{Rykhlevskii, A.}, Tsofin, V. ``Comparing fast neutron transport calculations using code package KATRIN-2.0 for various options of VVER-440 core setup.''
         \textbf{Scientific and technical conference of young specialists.}
         Podolsk, Russia. March, 2011.
	\end{bibenum}
%__________________________________________________________________________________________________________________
% Conference Publications
    \section{\mysidestyle Refereed\\Conference\\Abstracts}
    \begin{bibenum} 
    \item \textbf{Rykhlevskii, A.}, Lindsay, A., Huff, K. ``Simulation of Molten Salt Reactors with Moltres.'' \textbf{2019 SIAM Conference on Computational Science and Engineering}, 
            Spokane, WA, February 2019.
	\item \textbf{Rykhlevskii, A.}, Betzler, B.R., Bae, J.W., Huff, K. ``Fuel Cycle Performance of Fast Spectrum Molten Salt Reactor Designs.'' (poster)
            \textbf{Oak Ridge National Laboratory Nuclear Engineering Science Laboratory Synthesis Poster Session.} 
            Oak Ridge, TN, United States, 2018.
    \item \textbf{Rykhlevskii, A.}, Huff, K. ``Computational Tools for Advanced 
            Molten Salt Reactor Simulation.'' \textbf{Blue Waters Symposium}, 
            Sun River, OR, June 2018.
	\end{bibenum}
% Technical Reports
\section{\mysidestyle Technical\\Reports}
\begin{bibenum} 
	\item \textbf{Rykhlevskii, A.}, Huff, K. ``Milestone 2.1 Report: 
	Demonstration of 
	SaltProc.'' \textbf{Advanced Reactors and Fuel Cycles Report Series}, 
	Nuclear Plasma and Radiological Engineering, University of Illinois.  
	Report UIUC-ARFC-2019-04, \url{https://doi.org/10.5281/zenodo.3355649},   
	Jun. 2019.  
\end{bibenum}
% Other Publications
\section{\mysidestyle Theses}
\begin{bibenum}
	\item \textbf{Rykhlevskii, A.} Fuel Processing Simulation Tool for 
	Liquid-fueled Nuclear Reactors.
	Doctoral dissertation. University of Illinois at Urbana-Champaign. In 
	progress.
	\item \textbf{Rykhlevskii, A.} Advanced  Online Fuel Reprocessing 
Simulation for Thorium-fueled Molten Salt Breeder Reactor.
M.Sc. thesis. University of Illinois at Urbana-Champaign.  May 2018.
\end{bibenum}
%__________________________________________________________________________________________________________________
% Software Products
\section{\mysidestyle Software\\Products}
\begin{bibenum}
	\item \textbf{Rykhlevskii, A.}, Bae, J.W., Huff, K. ``SaltProc v0.2.'' 
	\textbf{zenodo}, July 2018.
	\url{http://dx.doi.org/10.5281/zenodo.1196454}.
	
	\item Lindsay, A., Huff, K., \textbf{Rykhlevskii, A.} ``moltres v0.1.'' 
	\textbf{zenodo}, June 2017. \url{http://dx.doi.org/10.5281/zenodo.801823}.
	
	\item Bates, C., Biondo, E., Brachem, C., Carlsen, R., Cary, J., Davis, 
	A., Dembia, C., Elfring, M., Flanagan, R., Gidden, M., Haines, T., 
	Howland, J., Huff, K., Jackson, S., Kiesling, K., Klebenow, M., Kuett, M., 
	Manalo, K., M. McCormick, A. Opotowsky, C., Pavlovsky, R., Rabbani, M., 
	Relson, E., Romano, P., \textbf{Rykhlevskii, A.}, Scopatz, A., Shriwise, 
	P., Slaybaugh, R., Wilson, P., Xia, J., J. Zachman, C., and Zweig, M. 
	``PyNE v0.5.11.'' \textbf{github}. 
	github.com/pyne/pyne/releases/tag/0.5.11. March 2018. 
\end{bibenum}

\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

